---
title: "Week 1 of R Programming"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

# Data Types - R Objects
atomic (basic) classes of objects: character, numeric, integer, complex, logical

# Data Types - Vectors and lists

## Creating vectors
Vectors will be coerced to the atomic class that is the least common demoninatory (i.e. if numeric and character you'll get a character vector)

```{r}

x<- c(0.5, 0.6)
y<- 9:29
z<- c(5, TRUE, "hello") # Coercion - 

#Explicit coercion

x<- 0:6
class(x)
as.numeric(x)
class(x)
as.logical(x)
as.character(x)

```

# Lists
Every object can be a different type of class

Elements are indexed with [[]]

# Matrices
Special type of vector (not a specific class) vectors with a dimension attribute

```{r}
m <- matrix(nrow = 2, ncol = 3)
m <- matrix(1:6, nrow = 2, ncol = 3)
n<- 1:10
dim(n) <- c(2,5)

x <- 1:3
y <- 10:12
cbind(x,y)
rbind(x,y)
```
# Factors - 
Special vector that represents categorical data

Ordered or unordered 

```{r}
data<-read.csv("hw1_data.csv")
```

```{r}
summary(data)
```

